The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2013-10-06 bmc_article.tex
More papers

Recent prominent use cases of the CDK~\cite{Steinbeck2003,Steinbeck2006} \ldots (EGON)
AMBIT, ScaffoldHunter, OMG, Padel, ...

Plugins for Taverna, KNIME, ...

>>>>

Recent prominent use cases of the CDK~\cite{Steinbeck2003,Steinbeck2006} \ldots (EGON)
AMBIT~\cite{jeliazkova2011ambit}, jCompoundMapper~\cite{Hinselmann2011},
ScaffoldHunter~\cite{wetzel2009interactive}, OMG~\cite{Peironcely2012}, Padel~\cite{yap2011padel}, ...

Plugins for Taverna\cite{Truszkowski2011}, KNIME\cite{Beisken2013}, ...

Some extensions make it back into the main library, like SMSD~\cite{} and fingerprints from Padel.
Not all extensions made it back into the main library, such as those from
AMBIT-SMARTS~\cite{jeliazkova2011ambitsmarts}, AMBIT-Tautomer~\cite{kochev2013ambit}, FooFromRydberg~\cite{}.
